Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-21 paper/snakemajoranas.tex
fix figure ref

\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:bandstructures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part eventually scatters with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface increases.

>>>>

\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:band_structures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part eventually scatters with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface increases.
